Gammapy: A Python package for gamma-ray astronomy

### 2023-05-24 src/ms-review.tex
Add links to detailed broadband SED fitting examples

>>>>

More examples for modelling the broadband emission of \gammaray sources, which 
partly involve \gammpy are available in the online documentation of the
Agnpy, Naima, Jetset and Gamera packages\footnote{\url{https://agnpy.readthedocs.io/en/latest/tutorials/ssc_gammapy_fit.html}},
\footnote{\url{https://naima.readthedocs.io/en/stable/tutorial.html}}, 
\footnote{\url{https://jetset.readthedocs.io/en/stable/user_guide/documentation_notebooks/gammapy_plugin/gammapy_plugin.html}},
\footnote{\url{http://libgamera.github.io/GAMERA/docs/fitting_data.html}}.
